---
title: "Comb_real"
output: html_document
date: "2023-05-19"
---

```{r, setup, message=FALSE}
## load up the packages we will need: 
library(tidyverse)
library(dplyr)
library(gt)
# for putting ggplots together
library(patchwork)
# for reordering facctors in ggplot
library(forcats)
library(kableExtra)
library(readr)

options(knitr.table.format = "html") 
```

```{r,message=FALSE}
#### Univariate regressions
Ins_Mod_Uni <- read_csv("~/Desktop/Coding/data/Ins_Mod_Uni.csv")
Ins_Act_Uni <- read_csv("~/Desktop/Coding/data/Ins_Act_Uni.csv")
Act_Mod_Uni <- read_csv("~/Desktop/Coding/data/Act_Mod_Uni.csv")

#### With Covariates
Ins_Mod <- read_csv("~/Desktop/Coding/data/Ins_Mod.csv")
Ins_Act <- read_csv("~/Desktop/Coding/data/Ins_Act.csv")
Act_Mod <- read_csv( "~/Desktop/Coding/data/Act_Mod.csv")
```

```{r}
#create the variable within the dataframe
Ins_Mod <- mutate(Ins_Mod, order = 0)
#update the values of the dataset to reflect the order we want
Ins_Mod[1,9]  = 2
Ins_Mod[2,9]  = 3
Ins_Mod[3,9]  = 4
Ins_Mod[4,9]  = 5
Ins_Mod[5,9]  = 6
Ins_Mod[6,9]  = 7
Ins_Mod[7,9]  = 8
Ins_Mod[8,9]  = 9
Ins_Mod[9,9]  = 10
Ins_Mod[10,9] = 11
Ins_Mod[11,9] = 12
Ins_Mod[12,9] = 13
Ins_Mod[13,9] = 14
Ins_Mod[14,9] = 15
Ins_Mod[15,9] = 16
Ins_Mod[16,9] = 17
Ins_Mod[17,9] = 18
Ins_Mod[18,9] = 19
Ins_Mod[19,9] = 20
Ins_Mod[20,9] = 21
Ins_Mod[21,9] = 22
Ins_Mod[22,9] = 23
Ins_Mod[23,9] = 24

# create a varaible for significance 
Ins_Mod <- mutate(Ins_Mod, sig = 1)

#create a variable for what it is
Ins_Mod <- mutate(Ins_Mod, Contrast = "Insufficient vs Moderate")
```

```{r}
# assign values to the significant models post alpha corrections.
Ins_Mod[1,10] = 19
Ins_Mod[3,10] = 19
Ins_Mod[5,10] = 19
Ins_Mod[21,10] = 19

Ins_Mod
```

We are going to split these conditions into a mental and physical health dataframes.
because `ggplot()` gets mad when we try to arrange these all together. Here ou can see an example of the dataframe with the order and significance. 
```{r}
phc_IM <- Ins_Mod[1:17,]
mhc_IM <- Ins_Mod[18:23,]
knitr::kable(phc_IM) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
knitr::kable(mhc_IM) %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```
Now we have a data frame for physical health conditions and a data frame for mental 
health conditions. We will repeat these steps for the other 2 full models, and the 3 univariate models.

```{r, include=FALSE}
Ins_Act <- mutate(Ins_Act, order = 0)
Ins_Act[1,9]  = 2
Ins_Act[2,9]  = 3
Ins_Act[3,9]  = 4
Ins_Act[4,9]  = 5
Ins_Act[5,9]  = 6
Ins_Act[6,9]  = 7
Ins_Act[7,9]  = 8
Ins_Act[8,9]  = 9
Ins_Act[9,9]  = 10
Ins_Act[10,9] = 11
Ins_Act[11,9] = 12
Ins_Act[12,9] = 13
Ins_Act[13,9] = 14
Ins_Act[14,9] = 15
Ins_Act[15,9] = 16
Ins_Act[16,9] = 17
Ins_Act[17,9] = 18
Ins_Act[18,9] = 2
Ins_Act[19,9] = 3
Ins_Act[20,9] = 4
Ins_Act[21,9] = 5
Ins_Act[22,9] = 6
Ins_Act[23,9] = 7
Ins_Act

Ins_Act <- mutate(Ins_Act, sig = 1)
Ins_Act[1,10] = 19
Ins_Act[3,10] = 19
Ins_Act[5,10] = 19
Ins_Act[6,10] = 19
Ins_Act[9,10] = 19
Ins_Act[17,10] = 19
Ins_Act[22,10] = 19

Ins_Act <- mutate(Ins_Act, Contrast = "Insufficient vs Active")
phc_IA <- Ins_Act[1:17,]
mhc_IA <- Ins_Act[18:23,]

Act_Mod <- mutate(Act_Mod, order = 0)
Act_Mod[1,9] = 2
Act_Mod[2,9] = 3
Act_Mod[3,9] = 4
Act_Mod[4,9]  = 5
Act_Mod[5,9]  = 6
Act_Mod[6,9]  = 7
Act_Mod[7,9]  = 8
Act_Mod[8,9]  = 9
Act_Mod[9,9]  = 10
Act_Mod[10,9] = 11
Act_Mod[11,9] = 12
Act_Mod[12,9] = 13
Act_Mod[13,9] = 14
Act_Mod[14,9] = 15
Act_Mod[15,9] = 16
Act_Mod[16,9] = 17
Act_Mod[17,9] = 18
Act_Mod[18,9] = 2
Act_Mod[19,9] = 3
Act_Mod[20,9] = 4
Act_Mod[21,9] = 5
Act_Mod[22,9] = 6
Act_Mod[23,9] = 7

Act_Mod <- mutate(Act_Mod, sig = 1)
Act_Mod <- mutate(Act_Mod, Contrast = "Active vs Moderate")
phc_AM <- Act_Mod[1:17,]
mhc_AM <- Act_Mod[18:23,]
```

Long data
```{r}
PHC_long <- rbind(phc_IA, phc_IM, phc_AM)
MHC_long <- rbind(mhc_IA, mhc_IM, mhc_AM)

PHC_long
```
ggforestplot
```{r}

# p <- 
  PHC_long |>
  #Plot the value variable (in descending order) assigning significance to the 
  #values significant after Bon foroni alpha corrections
  ggplot(aes(y = reorder(variable, -order), color = as.factor(Contrast))) +
    geom_stripes(odd = "lightgrey", even = "white") +
  #take away background
    theme_classic() +
  #make the forrest plot
    geom_point(aes(x=estimate), shape= 19,  size=1.75,show.legend = FALSE, position = position_dodge2(width = 1)) +
  #geom_point(aes(x=estimate), shape= ifelse(PHC_long$sig ==19, 19, 1),  size=1.5,show.legend = FALSE, position = position_dodge2(width = 1))+
  geom_linerange(aes(xmin=conf.low, xmax=conf.high),show.legend = FALSE, position = position_dodge2(width = 1)) +
  #geom_errorbar(aes(xmin=conf.low, xmax=conf.high),width =.5)+
  #add color 
  #scale_color_manual(values = c("#A6A6A6","blue"))+
  #change Cordinates
  labs(x="Odds Ratio") +
  #adjust the dimentions. 
  coord_cartesian(ylim = c(1,18), xlim=c(0, 3)) +
  #add a line at 0 for reference 
  geom_vline(xintercept = 1, linetype="dashed") +
  #add anotations to help suggests what each side means.
  annotate("text", x = .5, y = 18, label = "Less Likely", size = 3.5) +
  annotate("text", x = 1.5, y = 18, label = "More Likely", size = 3.5) +
  #Git rid of the Y - Axis
  theme(axis.line.y = element_blank(),
        axis.ticks.y= element_blank(),
        # axis.text.y= element_blank(),
         axis.title.y= element_blank(),
        legend.position = "none")
```
```




