---
title: "Multinomial_output"
output: html_document
date: "2023-04-04"
---
```{r setup, include=FALSE}
# Thesis Preliminary Analyses
  #data stuff
library(tidyverse)
library(dplyr)
  #CSV/CAV files
library(haven)
  #EDA stuff

## Prepare Data For Analysis 

#### Import & Select data

### Import dataset 
setwd("~/Desktop/Adams_lab/SPSS_stuff")
NHRVS_2019 <- read_sav("~/Desktop/Adams_lab/SPSS_stuff/NHRVS_2019_2020_FINAL_weighted.sav")

### Select and rename Variables
thesis_NHRVS <- dplyr::select(NHRVS_2019,
    #Background Variables __________
      caseid,weight,Age,Male_Gender,White_Race,SomeCollege_or_Higher,
      Married_Partnered,Income_60k_plus,YN_work,
      PCS_FINAL,MCS_FINAL,Weight_kg,BMI,
    #Military variables__________
      Combat_Veteran,Years_in_Military,Branch_5cat,Enlistment_status_3cat,
      MilitaryRank_3cat,
    #Mental Health Variables___________
      TOTAL_TRAUMAS,LT_PCL_33,LT_MDD_Sx_only,LT_Suicide_4cat,Suicide_Attempt_LT,
      LT_Suicide_Plan,LT_AUD,LT_NicotineDep,LT_DUD,tot_MHC,Any_MHC,
    #Physical health Variables_________
      ANY_ADL_DISABILITY,ANY_IADL_DISABILITY,Any_Disability,tot_phc,Any_PHC,Q22A_1,Q22A_2,
      Q22A_3,Q22A_4,Q22A_5,Q22A_6,Q22A_7,Q22A_8,Q22A_9,Q22A_10,Q22A_11,Q22B_1,
      Q22B_2,Q22B_3,Q22B_4,Q22B_5,
    #Exercise variables ___________
      godin_mild_winsor,godin_Mod_winsor,godin_Stren_winsor,HCS,HCS_Cats,
      godin_total_ac,god3cat,god2cat,GODIN_outliers)
    
#Rename variabes
thesis_NHRVS <- rename(thesis_NHRVS,
      MET_total = godin_total_ac,
      God_mild = godin_mild_winsor,
      God_mod = godin_Mod_winsor,
      God_stren = godin_Stren_winsor,
      College = SomeCollege_or_Higher,
      MCS = MCS_FINAL,
      PCS = PCS_FINAL,
      Arthritis = Q22A_1,
      Athsma =  Q22A_2,
      Cancer = Q22A_3,
      Chron_pain = Q22A_4,
      Liv_dis = Q22A_5,
      Diabetes = Q22A_6,
      Hrt_dis = Q22A_7,
      Hrt_atk = Q22A_8,
      High_chol = Q22A_9,
      High_bld_press = Q22A_10,
      Kid_dis = Q22A_11,
      Migrane = Q22B_1,
      MS = Q22B_2,
      Osteoporosis = Q22B_3,
      Rhum_arth = Q22B_4,
      Stroke = Q22B_5,
      LT_MDD = LT_MDD_Sx_only,
      LT_PTSD = LT_PCL_33
)
# We need exercsie variables that are in MET minutes, not just HCS. 
# We also need to create demographic and health variables

thesis_NHRVS<- thesis_NHRVS %>%
  # First Create all of the variables
  mutate(thesis_NHRVS, 
    # Exercise variables
         Ex_time = (God_mild + God_mod + God_stren)*15,
            # Tells us how long people exercised for.
         MET_min = MET_total* 15,
         MET_min_W = ifelse(MET_min > 2500, 2500, MET_min),
            # Total METs per week times the duration of exercise
         Ex_rec = as.factor(ifelse(MET_min >= 500, "Sufficient", "Insufficient")),
            # Meeting activity levels (i.e., sufficient vs insufficient)
         Ex_3cat = as.factor(ifelse(MET_min < 290, 1,
                              ifelse(MET_min < 500 & MET_min >= 290, 2,3))),
         Ex_4cats = as.factor(ifelse(MET_min < 290, "Sed",
                              ifelse(MET_min < 500 & MET_min >= 290, "Mod",
                              ifelse(MET_min < 1000 & MET_min >= 500, "Active", 
                              ifelse(MET_min < 2000 & MET_min >= 1000, "Super", NA))))),
         Ex_3catW = as.factor(ifelse(MET_min_W < 290, 1,
                              ifelse(MET_min_W < 500 & MET_min_W >= 290, 2,3))),
         Ex_4catsW = as.factor(ifelse(MET_min_W < 290, "Sed",
                              ifelse(MET_min_W < 500 & MET_min_W >= 290, "Mod",
                              ifelse(MET_min_W < 1000 & MET_min_W >= 500, "Active", 
                              ifelse(MET_min_W < 2500 & MET_min_W >= 1000, "Super", NA))))),
# 3 godin (HCS) categories converted to MET_min 
    # Other Variables 
         HCS_win = (God_mod*5) + (God_stren*9),
         HCS3cat = as.factor(ifelse(HCS_win < 14, "Insufficient",
                              ifelse(HCS_win < 24 & HCS_win >= 290, "Moderate", "Active"))),
         Yr5_Military = as.factor(ifelse(Years_in_Military >= 5, "5+", "<5")),
         Active_PA = as.factor(ifelse(Ex_3cat == 3,1,0)),
         Moderate_PA = as.factor(ifelse(Ex_3cat == 2,1,0)),
         Insuf_PA = as.factor(ifelse(Ex_3cat == 2,1,0)),
         Total_HC = Any_Disability + Arthritis + Cancer + Chron_pain + Liv_dis +
                    Diabetes + Hrt_dis + Hrt_atk + High_chol + High_bld_press +
                    Kid_dis + Migrane + MS + Osteoporosis + Rhum_arth + Stroke +
                    LT_MDD + LT_PTSD + LT_AUD + LT_DUD + LT_NicotineDep,
         Total_PHC = Any_Disability + Arthritis + Cancer + Chron_pain + Liv_dis +
                    Diabetes + Hrt_dis + Hrt_atk + High_chol + High_bld_press +
                    Kid_dis + Migrane + MS + Osteoporosis + Rhum_arth + Stroke,
        Total_MHC = LT_MDD + LT_PTSD + LT_AUD + LT_DUD + LT_NicotineDep,
    
    ) %>%
mutate(thesis_NHRVS,
      #Physical health variables
           Any_Disability = as.factor(Any_Disability),
           Arthritis = as.factor(Arthritis),
           Athsma = as.factor(Athsma),
           Cancer = as.factor(Cancer),
           Chron_pain = as.factor(Chron_pain),
           Liv_dis = as.factor(Liv_dis),
           Diabetes = as.factor(Diabetes),
           Hrt_dis = as.factor(Hrt_dis),
           Hrt_atk = as.factor(Hrt_atk),
           High_chol = as.factor(High_chol),
           High_bld_press = as.factor(High_bld_press),
           Kid_dis = as.factor(Kid_dis),
           Migrane = as.factor(Migrane),
           MS = as.factor(MS),
           Osteoporosis = as.factor(Osteoporosis),
           Rhum_arth = as.factor(Rhum_arth),
           Stroke = as.factor(Stroke),
           Ex_3cat = as.factor(Ex_3cat),  
           Male_Gender = as.factor(Male_Gender), 
           Married_Partnered = as.factor(Married_Partnered),
           White_Race = as.factor(White_Race),
           College = as.factor(College),
           Income_60k_plus = as.factor(Income_60k_plus),
           YN_work = as.factor(YN_work),
           Combat_Veteran = as.factor(Combat_Veteran),
           Any_MHC = as.factor(Any_MHC),
           Any_PHC = as.factor(Any_PHC),
           god2cat = as.factor(god2cat),
      #Mental health variables
          LT_Suicide_4cat = as.factor(LT_Suicide_4cat),
          LT_MDD = as.factor(LT_MDD),
          LT_PTSD = as.factor(LT_PTSD),
          LT_AUD = as.factor(LT_AUD),
          LT_DUD = as.factor(LT_DUD),
          LT_NicotineDep = as.factor(LT_NicotineDep)
    )
thesis_NHRVS <- mutate(thesis_NHRVS, 
        Ex_3cat = recode(Ex_3cat,
                         "1" = "Insufficient",
                         "2" = "Moderate",
                         "3" = "Active"),
        Married_Partnered = recode(Married_Partnered,
                         "0" = "Married_Partnered",
                         "1" = "Single"),
        Male_Gender = as.factor(Male_Gender),
        Male_Gender = recode(Male_Gender,
                         "0" = "Female",
                         "1" = "Male"),
        White_Race = recode(White_Race,
                         "0" = "Not_White",
                         "1" = "White"),
        College = recode(College,
                         "0" = "No_Colege",
                         "1" = "Some_Colege"),
        Income_60k_plus = recode(Income_60k_plus,
                         "0" = "Under_60k",
                         "1" = "OVer_60k"),
        YN_work = recode(YN_work,
                         "1" = "No_Work",
                         "2" = "Working"),
        Combat_Veteran = as.factor(Combat_Veteran),
        Combat_Veteran = recode(Combat_Veteran,
                         "0" = "No_Combat",
                         "1" = "Combat"),
        Any_MHC = recode(Any_MHC,
                         "0" = "No_con",
                         "1" = "MHC"),
        Any_PHC = recode(Any_PHC,
                         "0" = "No_con",
                         "1" = "PHC"),
        LT_Suicide_4cat = as.factor(LT_Suicide_4cat),
        LT_Suicidal = recode(LT_Suicide_4cat,
                         "0" = "0",
                         "1" = "0",
                         "2" = "1",
                         "3" = "1"
                             ))

#Filter out NA values
thesis_NHRVS <- thesis_NHRVS %>%
  filter(!is.na(Ex_rec)) %>%
  filter(!is.na(Ex_3cat)) %>%
  filter(!is.na(MCS)) %>%
  filter(!is.na(PCS)) %>%
  filter(!is.na(BMI)) %>%
  filter(!is.na(Any_Disability)) %>%
  filter(!is.na(Arthritis)) %>%
  filter(!is.na(Cancer)) %>%
  filter(!is.na(Chron_pain)) %>%
  filter(!is.na(Liv_dis)) %>%
  filter(!is.na(Diabetes)) %>%
  filter(!is.na(Hrt_dis)) %>%
  filter(!is.na(Hrt_atk)) %>%
  filter(!is.na(High_chol)) %>%
  filter(!is.na(High_bld_press)) %>%
  filter(!is.na(Kid_dis)) %>%
  filter(!is.na(Migrane)) %>%
  filter(!is.na(MS)) %>%
  filter(!is.na(Osteoporosis)) %>%
  filter(!is.na(Rhum_arth)) %>%
  filter(!is.na(Stroke)) %>%
  filter(!is.na(LT_MDD)) %>%
  filter(!is.na(LT_PTSD)) %>%
  filter(!is.na(LT_AUD)) %>%
  filter(!is.na(LT_DUD)) %>%
  filter(!is.na(LT_NicotineDep)) %>%
  filter(!is.na(LT_Suicidal))
#$View(thesis_NHRVS)
thesis_NHRVS
library(MASS)
library(nnet)
```
### Odds ratios of health conditions without covariates.
This will help us establish if our covariates are suppressing or negatively impacting the relationship of these variabes on our dependent variable (exericse)
```{r}
#First make empty data frame
variable = 0
IM_OR = 0
IA_OR = 0
AM_OR = 0
uni_check <- data.frame(variable, IA_OR, IM_OR, AM_OR)
```


```{r}
#univariate multinomial stuff
uni_OR_tab<-function(Data,condition,string){
#1. Model 1
df <- multinom(relevel(Ex_3cat,ref = "Insufficient")  ~ condition, data = Data)
#2. Model 2
df2 <- multinom(relevel(Ex_3cat,ref = "Active") ~ condition, data = Data)
#3. Odds ratio
  OR_df <- exp(coef(df))
  OR_df2 <- exp(coef(df2))
#4. assign values 
variable = string
IM_OR= OR_df[[3]]
IA_OR = OR_df[[4]]
AM_OR = OR_df2[[4]]
output<-data.frame(variable, IA_OR, IM_OR, AM_OR)
#return output
return(output)
}
```

Run univariate function
```{r}
uni_check<-rbind(uni_check,uni_OR_tab(thesis_NHRVS,thesis_NHRVS$Any_Disability,"Any Disability"))
uni_check<-rbind(uni_check,uni_OR_tab(thesis_NHRVS,thesis_NHRVS$Arthritis,"Arthritis"))
uni_check<-rbind(uni_check,uni_OR_tab(thesis_NHRVS,thesis_NHRVS$Athsma,"Athsma"))
uni_check<-rbind(uni_check,uni_OR_tab(thesis_NHRVS,thesis_NHRVS$Cancer,"Cancer"))
uni_check<-rbind(uni_check,uni_OR_tab(thesis_NHRVS,thesis_NHRVS$Chron_pain,"Chronic Pain"))
uni_check<-rbind(uni_check,uni_OR_tab(thesis_NHRVS,thesis_NHRVS$Hrt_atk,"Heart Attack"))
uni_check<-rbind(uni_check,uni_OR_tab(thesis_NHRVS,thesis_NHRVS$Hrt_dis,"Heart Disease"))
uni_check<-rbind(uni_check,uni_OR_tab(thesis_NHRVS,thesis_NHRVS$High_chol,"Hypertension"))
uni_check<-rbind(uni_check,uni_OR_tab(thesis_NHRVS,thesis_NHRVS$Kid_dis,"Kidney Disease"))
uni_check<-rbind(uni_check,uni_OR_tab(thesis_NHRVS,thesis_NHRVS$Liv_dis,"Liver Disease"))
uni_check<-rbind(uni_check,uni_OR_tab(thesis_NHRVS,thesis_NHRVS$Migrane,"Migrane"))
uni_check<-rbind(uni_check,uni_OR_tab(thesis_NHRVS,thesis_NHRVS$MS,"MS"))
uni_check<-rbind(uni_check,uni_OR_tab(thesis_NHRVS,thesis_NHRVS$Osteoporosis,"Osteoporosis"))
uni_check<-rbind(uni_check,uni_OR_tab(thesis_NHRVS,thesis_NHRVS$Rhum_arth,"RA"))
uni_check<-rbind(uni_check,uni_OR_tab(thesis_NHRVS,thesis_NHRVS$Stroke,"Stroke"))
uni_check<-rbind(uni_check,uni_OR_tab(thesis_NHRVS,thesis_NHRVS$LT_AUD,"AUD"))
uni_check<-rbind(uni_check,uni_OR_tab(thesis_NHRVS,thesis_NHRVS$LT_DUD,"DUD"))
uni_check<-rbind(uni_check,uni_OR_tab(thesis_NHRVS,thesis_NHRVS$LT_MDD,"MDD"))
uni_check<-rbind(uni_check,uni_OR_tab(thesis_NHRVS,thesis_NHRVS$LT_NicotineDep ,"Nicotine Dep"))
uni_check<-rbind(uni_check,uni_OR_tab(thesis_NHRVS,thesis_NHRVS$LT_PTSD,"PTSD"))
uni_check<-rbind(uni_check,uni_OR_tab(thesis_NHRVS,thesis_NHRVS$LT_Suicidal ,"Arthritis"))
uni_check<-rbind(uni_check,uni_OR_tab(thesis_NHRVS,thesis_NHRVS$Arthritis,"Arthritis"))
uni_check<-rbind(uni_check,uni_OR_tab(thesis_NHRVS,thesis_NHRVS$Arthritis,"Arthritis"))
uni_check<-rbind(uni_check,uni_OR_tab(thesis_NHRVS,thesis_NHRVS$Arthritis,"Arthritis"))
uni_check<-uni_check[(-1),]
uni_check
```
### Write a CSV file to store these values
```{r}
write.csv(uni_check,"~/Desktop/Coding/data/uni_check.csv")
```

## Odds Ratios and R^2 change tables 
```{r}
#1. Import tables
  Ins_Mod <- read_csv("~/Desktop/Coding/data/Ins_Mod.csv")
  Ins_Act <- read_csv("~/Desktop/Coding/data/Ins_Act.csv")
  Act_Mod <- read_csv( "~/Desktop/Coding/data/Act_Mod.csv")

#2. Create dataframe
  OR_Table = data.frame(
      Ins_Act$variable, Ins_Act$ci, Ins_Mod$ci, Act_Mod$ci, Ins_Act$r2_change
      )
  colnames(OR_Table) <- c("Helath Condition","Insufficient vs Sufficient ORs",
                          "Insufficient vs Moderate ORs", "Active vs Moderate ORs", "R^2 Change")
#3. View Table
    OR_Table

#4 Export Table
    write_csv(OR_Table,"~/Desktop/Coding/data/Thesis_OR_Table.csv")
```
## Odds ratios and R^2 of covariates 
This code creates a table displaying output for covariates for the multinomial model

## difference between SF8 and withouot
```{r,results='hide'}
library(performance)
Cov_big<-multinom(relevel(Ex_3cat,ref = "Insufficient")  ~ Age + College + Income_60k_plus + YN_work + BMI, data = thesis_NHRVS)
Cov_big2<-multinom(relevel(Ex_3cat,ref = "Insufficient")  ~ Age + College + Income_60k_plus + YN_work + BMI, data = thesis_NHRVS)

Cov_big_full<-multinom(relevel(Ex_3cat,ref = "Insufficient") ~ Age + College + Income_60k_plus + YN_work + BMI + MCS, data = thesis_NHRVS)
Cov_big2_full<-multinom(relevel(Ex_3cat,ref = "Insufficient")  ~  Age + College + Income_60k_plus + YN_work + BMI + PCS, data = thesis_NHRVS)

#r2 for big
R2_Cov_big <- performance::r2(Cov_big)
R2_Cov_big2 <- performance::r2(Cov_big2)

#r2 change
MCS_delta <-  (r2(Cov_big_full)[[1]] -  r2(Cov_big)[[1]])*100
PCS_delta <-  (r2(Cov_big2_full)[[1]] -  r2(Cov_big2)[[1]])*100
```

So, By including MCS and PCS in the model we are explaining an additional 3% and .5% of the variance explained in exercise by the covariates.
```{r}
#report
MCS_delta
PCS_delta
```

```{r}
### Part 1 Create values for table
#1. Run the models
Cov_Reg<-multinom(relevel(Ex_3cat,ref = "Insufficient")  ~ Age + College + Income_60k_plus + YN_work + BMI, data = thesis_NHRVS)
Cov_Reg<-multinom(relevel(Ex_3cat,ref = "Active")  ~ Age + College + Income_60k_plus + YN_work + BMI, data = thesis_NHRVS)

#2. Coefficients 
  coefs_Cov_Reg <- abs(coef(Cov_Reg))
  coefs_Cov_Reg2 <- abs(coef(Cov_Reg2))
#3. Odds ratio
  OR_Cov_Reg <- exp(coef(Cov_Reg))
  OR_Cov_Reg2 <- exp(coef(Cov_Reg2))

#4. OR 95% CI
  CI_Cov_Reg <- data.frame(exp(confint(Cov_Reg)))
  CI_Cov_Reg2 <- data.frame(exp(confint(Cov_Reg2)))
#5. P value 
  P_value <- function(model) {
  z <- summary(model)$coefficients/summary(model)$standard.errors
  p <- (1 - pnorm(abs(z), 0, 1)) * 2
  return(p)
  }
  p_val1<- P_value(Cov_Reg)
  p_val2<- P_value(Cov_Reg2)
#6. R^2 for model
  R2_Cov_Reg <- performance::r2(Cov_Reg)
  R2_Cov_Reg2 <- performance::r2(Cov_Reg2)

  OR.CI_IvA <- paste(round(OR_Cov_Reg[2,2:5],2), "(",round(CI_Cov_Reg[2:5,3],2),"-", round(CI_Cov_Reg[2:5,4],2),")")
  OR.CI_IvM <- paste(round(OR_Cov_Reg[1,2:5],2), "(",round(CI_Cov_Reg[2:5,1],2),"-", round(CI_Cov_Reg[2:5,2],2),")")
  OR.CI_AvM <- paste(round(OR_Cov_Reg2[2,2:5],2),"(",round(CI_Cov_Reg2[2:5,3],2),"-", round(CI_Cov_Reg2[2:5,4],2),")")

#### Part 2. Make the table and export 

#1. Create data frame
cov_OR_tab <-  data.frame(cbind(
  variable = Cov_Reg$coefnames[2:length(Cov_Reg$coefnames)],
  IvA_ODDS = OR.CI_IvA,
  IvA_p = round(p_val1[2,2:5],4),
  IvM_ODDS = OR.CI_IvM,
  IvM_p = round(p_val1[1,2:5],4),
  AvM_ODDS = OR.CI_AvM, 
  AvM_p = round(p_val2[2,2:5],4)
))
#2. create the row for the R2
  paste("Covariates R^2 =", round((R2_Cov_Reg[[1]]*100),3),"%")
  variable = paste("Covariates R^2 =", round((R2_Cov_Reg[[1]]*100),3),"%")
  R2TAB<-data.frame(cbind(
                    variable, IvA_ODDS = NA, IvA_p = NA, IvM_ODDS = NA,
                    IvM_p = NA,AvM_ODDS = NA, AvM_p = NA))

#3. Bind the stuff together
  cov_OR_tab <- rbind(R2TAB, cov_OR_tab)
  cov_OR_tab

#4. Export
  write_csv(cov_OR_tab,"~/Desktop/Coding/data/cov_OR_tab.csv")
```


