---
title: "Preliminary Statistics"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---
The following code will show you the preliminary statistics ran before conducting regression analyses. This page includes:

1. Read in data, create new variables, clean data, and prepare data for analysis
2. Create visualiations depicting number of health conditions in each level of physical activity
3. Run exploratory data analysis examining the differences in sociodemographic & military factors based upon physical activity level. 
4. Create table displaying results of descriptive statistics (chi squaures, t tests, anovas) based upon physical activity level.

---
```{r,setup,message=FALSE}
options(knitr.table.format = "html") 

#data stuff
library(tidyverse)
library(dplyr)
  #CSV/CAV files
library(haven)
library(tableone)
  #regression stuff
library(aod)
library(gtsummary)
library(lmtest)
library(DescTools)
library(manipulate)
library(psych)
library(tableone)
library(kableExtra)
```

# Prep Data For Analyses

## {.tabset}

### Read and Select data

```{r}
### Import dataset 
NHRVS_2019 <- read_sav("~/Desktop/Adams_lab/SPSS_stuff/NHRVS_2019_2020_FINAL_weighted.sav")

### Select and rename Variables
thesis_NHRVS <- dplyr::select(NHRVS_2019,
    #Background Variables __________
      caseid,weight,Age,Male_Gender,White_Race,SomeCollege_or_Higher,
      Married_Partnered,Income_60k_plus,YN_work,
      PCS_FINAL,MCS_FINAL,Weight_kg,BMI,
    #Military variables__________
      Combat_Veteran,Years_in_Military,Branch_5cat,Enlistment_status_3cat,
      MilitaryRank_3cat,
    #Mental Health Variables___________
      TOTAL_TRAUMAS,LT_PCL_33,LT_MDD_Sx_only,LT_Suicide_4cat,Suicide_Attempt_LT,
      LT_Suicide_Plan,LT_AUD,LT_NicotineDep,LT_DUD,tot_MHC,Any_MHC,
    #Physical health Variables_________
      ANY_ADL_DISABILITY,ANY_IADL_DISABILITY,Any_Disability,tot_phc,Any_PHC,Q22A_1,Q22A_2,
      Q22A_3,Q22A_4,Q22A_5,Q22A_6,Q22A_7,Q22A_8,Q22A_9,Q22A_10,Q22A_11,Q22B_1,
      Q22B_2,Q22B_3,Q22B_4,Q22B_5,
    #Exercise variables ___________
      godin_mild_winsor,godin_Mod_winsor,godin_Stren_winsor,HCS,HCS_Cats,
      godin_total_ac,god3cat,god2cat,GODIN_outliers)
    
#Rename variabes
thesis_NHRVS <- rename(thesis_NHRVS,
      MET_total = godin_total_ac,
      God_mild = godin_mild_winsor,
      God_mod = godin_Mod_winsor,
      God_stren = godin_Stren_winsor,
      College = SomeCollege_or_Higher,
      MCS = MCS_FINAL,
      PCS = PCS_FINAL,
      Arthritis = Q22A_1,
      Athsma =  Q22A_2,
      Cancer = Q22A_3,
      Chron_pain = Q22A_4,
      Liv_dis = Q22A_5,
      Diabetes = Q22A_6,
      Hrt_dis = Q22A_7,
      Hrt_atk = Q22A_8,
      High_chol = Q22A_9,
      High_bld_press = Q22A_10,
      Kid_dis = Q22A_11,
      Migrane = Q22B_1,
      MS = Q22B_2,
      Osteoporosis = Q22B_3,
      Rhum_arth = Q22B_4,
      Stroke = Q22B_5,
      LT_MDD = LT_MDD_Sx_only,
      LT_PTSD = LT_PCL_33
)
```

### Create variables, rename stuff, and remove missing cases
```{r}
thesis_NHRVS<- thesis_NHRVS %>%
  # First Create all of the variables
  mutate(thesis_NHRVS, 
    # Exercise variables
         Ex_time = (God_mild + God_mod + God_stren)*15,
            # Tells us how long people exercised for.
         MET_min = MET_total* 15,
         MET_min_W = ifelse(MET_min > 2000, 2000, MET_min),
            # Total METs per week times the duration of exercise
         Ex_rec = as.factor(ifelse(MET_min >= 500, "Sufficient", "Insufficient")),
            # Meeting activity levels (i.e., sufficient vs insufficient)
         Ex_3cat = as.factor(ifelse(MET_min < 290, 1,
                              ifelse(MET_min < 500 & MET_min >= 290, 2,3))),
         Ex_4cats = as.factor(ifelse(MET_min < 290, "Sed",
                              ifelse(MET_min < 500 & MET_min >= 290, "Mod",
                              ifelse(MET_min < 1000 & MET_min >= 500, "Active", 
                              ifelse(MET_min < 2000 & MET_min >= 1000, "Super", NA))))),
# 3 godin (HCS) categories converted to MET_min 
    # Other Variables 
         HCS_win = (God_mod*5) + (God_stren*9),
         HCS3cat = as.factor(ifelse(HCS_win < 14, "Insufficient",
                              ifelse(HCS_win < 24 & HCS_win >= 290, "Moderate", "Active"))),
         Yr5_Military = as.factor(ifelse(Years_in_Military >= 5, "5+", "<5")),
         Active_PA = as.factor(ifelse(Ex_3cat == 3,1,0)),
         Moderate_PA = as.factor(ifelse(Ex_3cat == 2,1,0)),
         Insuf_PA = as.factor(ifelse(Ex_3cat == 2,1,0)),
         Total_HC = Any_Disability + Arthritis + Cancer + Chron_pain + Liv_dis +
                    Diabetes + Hrt_dis + Hrt_atk + High_chol + High_bld_press +
                    Kid_dis + Migrane + MS + Osteoporosis + Rhum_arth + Stroke +
                    LT_MDD + LT_PTSD + LT_AUD + LT_DUD + LT_NicotineDep,
         Total_PHC = Any_Disability + Arthritis + Cancer + Chron_pain + Liv_dis +
                    Diabetes + Hrt_dis + Hrt_atk + High_chol + High_bld_press +
                    Kid_dis + Migrane + MS + Osteoporosis + Rhum_arth + Stroke,
         Total_MHC = LT_MDD + LT_PTSD + LT_AUD + LT_DUD + LT_NicotineDep,
         No_Condition = ifelse(Any_MHC == 1 | Any_PHC ==1, 0,1)
    
    ) %>%

mutate(thesis_NHRVS,
      #Physical health variables
           Any_Disability = as.factor(Any_Disability),
           Arthritis = as.factor(Arthritis),
           Athsma = as.factor(Athsma),
           Cancer = as.factor(Cancer),
           Chron_pain = as.factor(Chron_pain),
           Liv_dis = as.factor(Liv_dis),
           Diabetes = as.factor(Diabetes),
           Hrt_dis = as.factor(Hrt_dis),
           Hrt_atk = as.factor(Hrt_atk),
           High_chol = as.factor(High_chol),
           High_bld_press = as.factor(High_bld_press),
           Kid_dis = as.factor(Kid_dis),
           Migrane = as.factor(Migrane),
           MS = as.factor(MS),
           Osteoporosis = as.factor(Osteoporosis),
           Rhum_arth = as.factor(Rhum_arth),
           Stroke = as.factor(Stroke),
           Ex_3cat = as.factor(Ex_3cat),  
           Male_Gender = as.factor(Male_Gender), 
           Married_Partnered = as.factor(Married_Partnered),
           White_Race = as.factor(White_Race),
           College = as.factor(College),
           Income_60k_plus = as.factor(Income_60k_plus),
           YN_work = as.factor(YN_work),
           Combat_Veteran = as.factor(Combat_Veteran),
           Any_MHC = as.factor(Any_MHC),
           Any_PHC = as.factor(Any_PHC),
           god2cat = as.factor(god2cat),
      #Mental health variables
          LT_Suicide_4cat = as.factor(LT_Suicide_4cat),
          LT_MDD = as.factor(LT_MDD),
          LT_PTSD = as.factor(LT_PTSD),
          LT_AUD = as.factor(LT_AUD),
          LT_DUD = as.factor(LT_DUD),
          LT_NicotineDep = as.factor(LT_NicotineDep)
      #Create a non health condition variable 
)%>%
mutate(thesis_NHRVS, 
        Ex_3cat = recode(Ex_3cat,
                         "1" = "Insufficient",
                         "2" = "Moderate",
                         "3" = "Active"),
        Married_Partnered = recode(Married_Partnered,
                         "0" = "Married_Partnered",
                         "1" = "Single"),
        Male_Gender = as.factor(Male_Gender),
        Male_Gender = recode(Male_Gender,
                         "0" = "Female",
                         "1" = "Male"),
        White_Race = recode(White_Race,
                         "0" = "Not_White",
                         "1" = "White"),
        College = recode(College,
                         "0" = "No_Colege",
                         "1" = "Some_Colege"),
        Income_60k_plus = recode(Income_60k_plus,
                         "0" = "Under_60k",
                         "1" = "OVer_60k"),
        YN_work = recode(YN_work,
                         "1" = "No_Work",
                         "2" = "Working"),
        Combat_Veteran = as.factor(Combat_Veteran),
        Combat_Veteran = recode(Combat_Veteran,
                         "0" = "No_Combat",
                         "1" = "Combat"),
        Any_MHC = recode(Any_MHC,
                         "0" = "No_con",
                         "1" = "MHC"),
        Any_PHC = recode(Any_PHC,
                         "0" = "No_con",
                         "1" = "PHC"),
        LT_Suicide_4cat = as.factor(LT_Suicide_4cat),
        LT_Suicidal = recode(LT_Suicide_4cat,
                         "0" = "0",
                         "1" = "0",
                         "2" = "1",
                         "3" = "1"
                             ))
#Filter out NA values
thesis_NHRVS <- thesis_NHRVS %>%
  filter(!is.na(Ex_rec)) %>%
  filter(!is.na(Ex_3cat)) %>%
  filter(!is.na(MCS)) %>%
  filter(!is.na(PCS)) %>%
  filter(!is.na(BMI)) %>%
  filter(!is.na(Any_Disability)) %>%
  filter(!is.na(Arthritis)) %>%
  filter(!is.na(Cancer)) %>%
  filter(!is.na(Chron_pain)) %>%
  filter(!is.na(Liv_dis)) %>%
  filter(!is.na(Diabetes)) %>%
  filter(!is.na(Hrt_dis)) %>%
  filter(!is.na(Hrt_atk)) %>%
  filter(!is.na(High_chol)) %>%
  filter(!is.na(High_bld_press)) %>%
  filter(!is.na(Kid_dis)) %>%
  filter(!is.na(Migrane)) %>%
  filter(!is.na(MS)) %>%
  filter(!is.na(Osteoporosis)) %>%
  filter(!is.na(Rhum_arth)) %>%
  filter(!is.na(Stroke)) %>%
  filter(!is.na(LT_MDD)) %>%
  filter(!is.na(LT_PTSD)) %>%
  filter(!is.na(LT_AUD)) %>%
  filter(!is.na(LT_DUD)) %>%
  filter(!is.na(LT_NicotineDep)) %>%
  filter(!is.na(LT_Suicidal))
 
kable(thesis_NHRVS[1:10,1:8]) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

### Export new file to CSV
Now that we have a clean and prepped data file to analyze lets create a CSV of that for future reference.
```{r}
write_csv(thesis_NHRVS, "~/Desktop/Coding/data/thesis_dataset.csv" )
haven::write_sav(thesis_NHRVS,"~/Desktop/Coding/data/thesis_SPSS.sav")
```


# Descriptives of Variables 

## {.tabset}

### Discriptive Table
Here are some discriptive statistics and basic plots to see an overview of the data. I use `table1()` to run the descriptive statistics.
```{r}
# Physical activity level value (MET minutes)
#install.packages("table1")

desc_tab<-data.frame(table1::table1(~MET_min_W + tot_MHC + tot_phc | Ex_3cat, data=thesis_NHRVS))
 knitr::kable(desc_tab) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

### Violin Plots
```{r}
#Plotting Met mins and Physical activity
ggplot(thesis_NHRVS, aes(x = Ex_3cat, y = MET_min_W)) +
  geom_violin()+
  geom_boxplot(width=0.1, color="blue", alpha=0.2)+
  ggtitle("Met minutes per physical activity level")

# Total Mental health conditions
ggplot(thesis_NHRVS, aes(x = Ex_3cat, y = tot_MHC)) +
  geom_violin()+
  geom_boxplot(width=0.1, color="blue", alpha=0.2) +
  ggtitle("Total number of mental health conditions by PA level")

# Total physical health conditions
ggplot(thesis_NHRVS, aes(x = Ex_3cat, y = tot_phc)) +
  geom_violin()+
  geom_boxplot(width=0.1, color="blue", alpha=0.2)+
  ggtitle("Total number of physical health conditions by PA level")
```
These descriptive are helpful for us to see how the data looks. Also it can be helpful to see what may be or not be wrong within the data


# Stacked Barcharts of health conditions 

## {.tabset}

### Cross tabs

I wanted to create a visualiation that depicted the number of veterans with or without health conditions within each physical activity level. The following code uses `xtabs()` to run cross tab/ chi squares. I start by extracting the number of veterans, and then convert the table into long data to plot the figure. 


Extracting values from chi square tables. 
```{r}
#table with and without health conditions
  AD_xtab2 <- xtabs(~Any_Disability +Ex_3cat,data = thesis_NHRVS)
  xtable2  <- rbind(AD_xtab2,xtabs(~Athsma+Ex_3cat,data = thesis_NHRVS))
  xtable2  <- rbind(xtable2,xtabs(~Arthritis+Ex_3cat,data = thesis_NHRVS))
  xtable2  <- rbind(xtable2,xtabs(~Cancer+Ex_3cat,data = thesis_NHRVS))
  xtable2  <- rbind(xtable2,xtabs(~Chron_pain+Ex_3cat,data = thesis_NHRVS))
  xtable2  <- rbind(xtable2,xtabs(~Liv_dis+Ex_3cat,data = thesis_NHRVS))
  xtable2  <- rbind(xtable2,xtabs(~Diabetes+Ex_3cat,data = thesis_NHRVS))
  xtable2  <- rbind(xtable2,xtabs(~Hrt_dis+Ex_3cat,data = thesis_NHRVS))
  xtable2  <- rbind(xtable2,xtabs(~Hrt_atk+Ex_3cat,data = thesis_NHRVS))
  xtable2  <- rbind(xtable2,xtabs(~High_chol+Ex_3cat,data = thesis_NHRVS))
  xtable2  <- rbind(xtable2,xtabs(~High_bld_press+Ex_3cat,data = thesis_NHRVS))
  xtable2  <- rbind(xtable2,xtabs(~Kid_dis+Ex_3cat,data = thesis_NHRVS))
  xtable2  <- rbind(xtable2,xtabs(~Migrane+Ex_3cat,data = thesis_NHRVS))
  xtable2  <- rbind(xtable2,xtabs(~MS+Ex_3cat,data = thesis_NHRVS))
  xtable2  <- rbind(xtable2,xtabs(~Osteoporosis+Ex_3cat,data = thesis_NHRVS))
  xtable2  <- rbind(xtable2,xtabs(~Rhum_arth+Ex_3cat,data = thesis_NHRVS))
  xtable2  <- rbind(xtable2,xtabs(~Stroke+Ex_3cat,data = thesis_NHRVS))
  xtable2  <- rbind(xtable2,xtabs(~LT_AUD+Ex_3cat,data = thesis_NHRVS))
  xtable2  <- rbind(xtable2,xtabs(~LT_DUD+Ex_3cat,data = thesis_NHRVS))
  xtable2  <- rbind(xtable2,xtabs(~LT_MDD+Ex_3cat,data = thesis_NHRVS))
  xtable2  <- rbind(xtable2,xtabs(~LT_PTSD+Ex_3cat,data = thesis_NHRVS))
  xtable2  <- rbind(xtable2,xtabs(~LT_NicotineDep+Ex_3cat,data = thesis_NHRVS))
  xtable2  <- rbind(xtable2,xtabs(~LT_Suicidal +Ex_3cat,data = thesis_NHRVS))
  xtable2  <- rbind(xtable2,xtabs(~No_Condition+Ex_3cat,data = thesis_NHRVS))
xtable2<-data.frame(xtable2)
#create a varaible for diagnosis
xtable2$condition<- NA
diagnose<- c("No Condition","Condition")
xtable2$condition = diagnose
knitr::kable(xtable2[1:10,]) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

```{r,include=FALSE}
  var_names = c("Any Disability",
                "Asthma",
                "Arthritis",
                "Cancer",
                "Chron pain",
                "Liver Disease",
                "Diabetes",
                "Heart Disease", 
                "Heart Attack", 
                "High Cholesterol", 
                "Hypertension", 
                "Kidney Disease", 
                "Migraine", 
                "MS", 
                "Osteoporosis", 
                "Rheumatoid Arthritis", 
                "Stroke",
                "AUD", 
                "DUD",
                "MDD", 
                "PTSD", 
                "Nicotine Dep", 
                "Suicidality",
                "No Condition")
```

### Create long dataset

Next I manually create a long dataset. I start by creating the variable names needed for the long dataset. 
```{r}
#2. Varaible names for table 
 var_names2 = c("Any Disability","Any Disability","Asthsma","Asthsma",
                "Arthritis", "Arthritis",
                "Cancer","Cancer",
                "Chron pain","Chron pain",
                "Liver Disease","Liver Disease",
                "Diabetes","Diabetes",
                "Heart Disease", "Heart Disease",
                "Heart Attack", "Heart Attack",
                "High Cholesterol", "High Cholesterol",
                "Hypertension", "Hypertension", 
                "Kidney Disease", "Kidney Disease",
                "Migraine",  "Migraine", 
                "MS", "MS", 
                "Osteoporosis", "Osteoporosis",
                "Rheumatoid Arthritis", "Rheumatoid Arthritis",
                "Stroke","Stroke",
                "AUD", "AUD", 
                "DUD","DUD",
                "MDD", "MDD", 
                "PTSD", "PTSD",
                "Nicotine Dep", "Nicotine Dep",
                "Suicidality","Suicidality",
                "No Condition", "No Condition")


#3. make long data frame (needed for plot)
      condition_df2          <- var_names2
      condition_df2 <- data.frame(condition_df2) 
      condition_df2[1:144,1]  <- var_names2              
      condition_df2[1:48,2]  <- xtable2$Insufficient
      condition_df2[1:48,3]  =  "Insufficient"
      condition_df2[49:96,2] <- xtable2$Moderate
      condition_df2[49:96,3] <- "Moderate"
      condition_df2[97:144,2] <- xtable2$Active
      condition_df2[97:144,3] =  "Sufficient"
      condition_df2$Diagnosis = xtable2$condition
      names(condition_df2) <- c("Variable","Value","Ex_3cat","Diagnosis")
      
      knitr::kable(condition_df2[1:10,]) %>%
         kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

### Stacked Barchart

Now that we have the data we can plot it! I use `ggplot()` to plot the figure. As this is a bar chart I use `geom_bar()` and use `position="stack"` to make the stacked bar chart. I used `fct_reorder()` to order the chart in order of the number of veterans reporting that condition. `facet_grid()` was used to seperate the the number of veterans with and without conditions into different figures. Lastly of note, I used `coord_flip()` to put both of the figures on the Y axis. 
```{r}
ggplot(condition_df2, aes(fill=Ex_3cat, y=Value, x= fct_reorder(Variable, Value))) + 
  geom_bar(position="stack", stat="identity")+
  facet_grid(~ Diagnosis)+ 
  ylab('Number of Veterans') +
  xlab('Health Condition')+
  labs(fill='Physical Activity') +
  theme_classic()+
  theme(legend.position="none")+
  coord_flip()
```

While this figure conveys what I want it to, it doesn't really help me interpret anything and looks bad in my opinion. I wanted to have both stacked bar charts on opposite sides of the variable names. Also I was unable to figure out how to reverse the X axis so I went into **_Illustrator_** and made the figure as I wanted it to look. Here is the final figure!

![Note. Stacked bar chart of the Number of veterans within each physical activity level between all health conditions. Total sample is observed between the left side of the figure (i.e., veterans who did not report health condition), and the right (i.e, veterans who did report a health condition) RA = Rheumatoid Arthritis, MS = Multiple Sclerosis, AUD = Alcohol Use Disorder, DUD = Drug Use Disorder, MDD = Major Depressive Disorder, Nicotine Dep = Nicotine Dependence, PTSD = Posttraumatic Stress Disorder. No Condition is reverse coded on the no condition figure (i.e., having a health condition).](images/Xtabs_thesis.png)

# Exploratory Data Analysis (EDA)
## {.tabset}
### Associations With Exercsie

The first step in our analysis is to figure out what sociodemographic / military characteristics are associated with differences in physical activity level (i.e., our dependent variable). I use `CreateTableOne()` to run the analyses as it will put everything in super nice table for me automatically. This table till tell me which covaaraites I need to use for my analysis.

```{r,results="hide"}
library(tableone)
EX_Vars <- c("Age", "Male_Gender", "White_Race", "College",     
                 "Married_Partnered", "Income_60k_plus", "YN_work", "PCS", 
                 "MCS", "Weight_kg", "BMI", "Combat_Veteran", 
                 "Yr5_Military", "TOTAL_TRAUMAS", "tot_phc", 
                 "tot_MHC")

EX_catVars     <- c("Male_Gender", "White_Race", "College",     
                 "Married_Partnered", "Income_60k_plus", "YN_work", "Combat_Veteran", 
                 "Yr5_Military","Ex_3cat")
Exercise_EDA <- CreateTableOne(vars = EX_Vars, strata = "Ex_3cat", data = thesis_NHRVS, 
               factorVars = EX_catVars)


full_sample<- CreateTableOne(vars = EX_Vars, data = thesis_NHRVS, 
               factorVars = EX_catVars)
full_sample <- print(full_sample, formatOptions = list(big.mark = ","))
test_tab <- print(Exercise_EDA, formatOptions = list(big.mark = ","))
Demo_tab <- cbind(full_sample, test_tab[,1:4])
```

```{r}
 knitr::kable(Demo_tab) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

This table lets us see differences between all of the variables for the exercise 
categories. If you look to the right of the Moderate category, you'll see the 
p-value for the tests done. The default test used by CreateTableOne are chi-squares
for categorical variables and a t-test for continuous variables.

These variables should be used for the regressions/ancovas 
  - Age,Some_college_or_higher, Income_60K_plus, YN_work, PCS_final or MCS_final,BMI

### Associations With Health Conditions
Next I am going to look at how covaaraites relate to both physical health and mental health conditions. I am going to repeat the same analysis as above with `CreateTableOne()` except I am changing `strata =` to any mental health condition (`"Any_MHC`) or any physical health condition (`Any_PHC`).
```{r,results="hide"}
MH_Vars <- c("Age", "Male_Gender", "White_Race", "College",     
                 "Married_Partnered", "Income_60k_plus", "YN_work", "PCS", 
                 "MCS", "Weight_kg", "BMI", "Combat_Veteran", 
                 "Yr5_Military", "TOTAL_TRAUMAS", "tot_phc", 
                 "tot_MHC")

MH_catVars     <- c("Male_Gender", "White_Race", "College",     
                 "Married_Partnered", "Income_60k_plus", "YN_work",   "Combat_Veteran", 
                 "Yr5_Military","Any_MHC")
MH_EDA <- CreateTableOne(vars = MH_Vars, strata = "Any_MHC", data = thesis_NHRVS, 
               factorVars = MH_catVars)


mh_tab <- print(MH_EDA, formatOptions = list(big.mark = ","))
Demo_tab <- cbind(Demo_tab,mh_tab[,1:3])

PH_Vars <- c("Age", "Male_Gender", "White_Race", "College",     
                 "Married_Partnered", "Income_60k_plus", "YN_work", "PCS", 
                 "MCS", "Weight_kg", "BMI", "Combat_Veteran", 
                 "Yr5_Military", "TOTAL_TRAUMAS", "tot_phc", 
                 "tot_MHC")

PH_catVars     <- c("Male_Gender", "White_Race", "College",     
                 "Married_Partnered", "Income_60k_plus", "YN_work", "Combat_Veteran", 
                 "Yr5_Military","Any_PHC")

PH_EDA <- CreateTableOne(vars = MH_Vars, strata = "Any_PHC", data = thesis_NHRVS, 
               factorVars = MH_catVars)

ph_tab <- print(PH_EDA, formatOptions = list(big.mark = ","))
Demo_tab <- cbind(Demo_tab,ph_tab[,1:3])
```

Now that I have created the tables, I can combine these with the physical activity level. The resulting table `Demo_tab` will be used in the paper. 
```{r}
Demo_tab<- as.data.frame(Demo_tab)
kbl(Demo_tab[1:10,]) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
write_csv(Demo_tab, "~/Desktop/Coding/data/Demo_tab_basic.csv")
```

# Tests of difference
This next section is extracting the F test score, _X^2_ test, and _t_ test values for the analysis above. These values will be used in the final demogrpahics table

### Physical activity levels 

Becasue some of the covariates are discrete variables while others are binary categorical/ non-binary categorical variables, I will be using `aov()` for ANOVAs, and using `summary()` to extract _F_ test, _t_ test, _X^2_ and  scores. As there is no function to run all of these together, I manually ran the analysis on all of the covariates and combined them into one table. Example of the code used for one covaraite is below:
```{r}
library(gmodels)
#### Create test of difference values and put them into a table

#Age
Age_test_act <- aov(Age~ Ex_3cat, data = thesis_NHRVS)
test_act_vars = c('Age')
Activity_val = c(summary(Age_test_act)[[1]]$`F value`[[1]])
Activity_p = c(summary(Age_test_act)[[1]]$`Pr(>F)`[[1]])
```

F test and chi square will be extracted for the remaining variables:
- Gender, White, some college, Married_partnered, Income 60k +, Working status, physical composite score, mental composite score, BMI, 5 years + in the military, total traumas, total physical health conditions, total mental health conditions.
```{r,include=FALSE}
#Gender
Male_test_act<- xtabs(~Ex_3cat+Male_Gender, data=thesis_NHRVS)
test_act_vars <- append(test_act_vars,'Male')
Activity_val <- append(Activity_val,summary(Male_test_act)[[3]])
Activity_p <- append(Activity_p,summary(Male_test_act)[[6]])

#White
White_test_act<- xtabs(~Ex_3cat+White_Race, data=thesis_NHRVS)
test_act_vars <- append(test_act_vars,'White')
Activity_val <- append(Activity_val,summary(White_test_act)[[3]])
Activity_p <- append(Activity_p,summary(White_test_act)[[6]])

#some College
College_test_act<- xtabs(~Ex_3cat+College, data=thesis_NHRVS)
test_act_vars <- append(test_act_vars,'College')
Activity_val <- append(Activity_val,summary(College_test_act)[[3]])
Activity_p <- append(Activity_p,summary(College_test_act)[[6]])

#Married_Partnered
Married_Partnered_test_act<- xtabs(~Ex_3cat+Married_Partnered, data=thesis_NHRVS)
test_act_vars <- append(test_act_vars,'Married_Partnered')
Activity_val <- append(Activity_val,summary(Married_Partnered_test_act)[[3]])
Activity_p <- append(Activity_p,summary(Married_Partnered_test_act)[[6]])

#Income_60k_plus
Income_60k_plus_test_act<- xtabs(~Ex_3cat+Income_60k_plus, data=thesis_NHRVS)
test_act_vars <- append(test_act_vars,'Income_60k_plus')
Activity_val <- append(Activity_val,summary(Income_60k_plus_test_act)[[3]])
Activity_p <- append(Activity_p,summary(Income_60k_plus_test_act)[[6]])

#YN_work
YN_work_test_act<- xtabs(~Ex_3cat+YN_work, data=thesis_NHRVS)
test_act_vars <- append(test_act_vars,'YN_work')
Activity_val <- append(Activity_val,summary(YN_work_test_act)[[3]])
Activity_p <- append(Activity_p,summary(YN_work_test_act)[[6]])

#PCS
PCS_test_act <- aov(PCS~ Ex_3cat, data = thesis_NHRVS)
test_act_vars <- append(test_act_vars,'PCS')
Activity_val <- append(Activity_val,summary(PCS_test_act)[[1]]$`F value`[[1]])
Activity_p <- append(Activity_p,summary(PCS_test_act)[[1]]$`Pr(>F)`[[1]])

#MCS
MCS_test_act <- aov(MCS~ Ex_3cat, data = thesis_NHRVS)
test_act_vars <- append(test_act_vars,'MCS')
Activity_val <- append(Activity_val,summary(MCS_test_act)[[1]]$`F value`[[1]])
Activity_p <- append(Activity_p,summary(MCS_test_act)[[1]]$`Pr(>F)`[[1]])

#BMI
BMI_test_act <- aov(BMI~ Ex_3cat, data = thesis_NHRVS)
test_act_vars <- append(test_act_vars,'BMI')
Activity_val <- append(Activity_val,summary(BMI_test_act)[[1]]$`F value`[[1]])
Activity_p <- append(Activity_p,summary(BMI_test_act)[[1]]$`Pr(>F)`[[1]])

#Combat_Veteran
Combat_Veteran_test_act<- xtabs(~Ex_3cat+Combat_Veteran, data=thesis_NHRVS)
test_act_vars <- append(test_act_vars,'Combat Veteran')
Activity_val <- append(Activity_val,summary(Combat_Veteran_test_act)[[3]])
Activity_p <- append(Activity_p,summary(Combat_Veteran_test_act)[[6]])

#Yr5_Military
Yr5_Military_test_act<- xtabs(~Ex_3cat+Yr5_Military, data=thesis_NHRVS)
test_act_vars <- append(test_act_vars,'5+ Years in Military')
Activity_val <- append(Activity_val,summary(Yr5_Military_test_act)[[3]])
Activity_p <- append(Activity_p,summary(Yr5_Military_test_act)[[6]])

#TOTAL TRAUMAS
TOTAL_TRAUMAS_test_act <- aov(TOTAL_TRAUMAS~ Ex_3cat, data = thesis_NHRVS)
test_act_vars <- append(test_act_vars,'TOTAL TRAUMAS')
Activity_val <- append(Activity_val,summary(TOTAL_TRAUMAS_test_act)[[1]]$`F value`[[1]])
Activity_p <- append(Activity_p,summary(TOTAL_TRAUMAS_test_act)[[1]]$`Pr(>F)`[[1]])

#TOTAL Physical Health Conditions
tot_phc_test_act <- aov(tot_phc~ Ex_3cat, data = thesis_NHRVS)
test_act_vars <- append(test_act_vars,'Total_PHC')
Activity_val <- append(Activity_val,summary(tot_phc_test_act)[[1]]$`F value`[[1]])
Activity_p <- append(Activity_p,summary(tot_phc_test_act)[[1]]$`Pr(>F)`[[1]])

#TOTAL Physical Health Conditions
tot_MHC_test_act <- aov(tot_MHC~ Ex_3cat, data = thesis_NHRVS)
test_act_vars <- append(test_act_vars,'Total MHC')
Activity_val <- append(Activity_val,summary(tot_MHC_test_act)[[1]]$`F value`[[1]])
Activity_p <- append(Activity_p,summary(tot_MHC_test_act)[[1]]$`Pr(>F)`[[1]])
```

Now that we have extracted all of the values, we can create a data frame for all of the test of difference values. We use `cbind()` to combine the test of difference values with the p values.
```{r}
val_df <- data.frame(test_act_vars,Activity_val)
val_df <- cbind(val_df,Activity_p)
```
#### Physical and Mental health Conditions
The same analysis will be conducted for these covariates by physical and mental health condition as well. 

```{r,include=FALSE}
#### Create test of difference values and put them into a table
#Age
PHC_val <- c(t.test(thesis_NHRVS$Age~thesis_NHRVS$Any_PHC)[[1]])
PHC_p <- c(t.test(thesis_NHRVS$Age~thesis_NHRVS$Any_PHC)[[3]])

#Gender
Male_test_PHC<- xtabs(~Any_PHC+Male_Gender, data=thesis_NHRVS)
summary(Male_test_PHC)
PHC_val <- append(PHC_val,Male_test_PHC[[3]])
PHC_p <- append(PHC_p,summary(Male_test_PHC)[[6]])

#White
White_test_PHC<- xtabs(~Any_PHC+White_Race, data=thesis_NHRVS)
PHC_val <- append(PHC_val,summary(White_test_PHC)[[3]])
PHC_p <- append(PHC_p,summary(White_test_PHC)[[6]])

#some College
College_test_PHC<- xtabs(~Any_PHC+College, data=thesis_NHRVS)
PHC_val <- append(PHC_val,summary(College_test_PHC)[[3]])
PHC_p <- append(PHC_p,summary(College_test_PHC)[[6]])

#Married_Partnered
Married_Partnered_test_PHC<- xtabs(~Any_PHC+Married_Partnered, data=thesis_NHRVS)
PHC_val <- append(PHC_val,summary(Married_Partnered_test_PHC)[[3]])
PHC_p <- append(PHC_p,summary(Married_Partnered_test_PHC)[[6]])

#Income_60k_plus
Income_60k_plus_test_PHC<- xtabs(~Any_PHC+Income_60k_plus, data=thesis_NHRVS)
PHC_val <- append(PHC_val,summary(Income_60k_plus_test_PHC)[[3]])
PHC_p <- append(PHC_p,summary(Income_60k_plus_test_PHC)[[6]])

#YN_work
YN_work_test_PHC<- xtabs(~Any_PHC+YN_work, data=thesis_NHRVS)
PHC_val <- append(PHC_val,summary(YN_work_test_PHC)[[3]])
PHC_p <- append(PHC_p,summary(YN_work_test_PHC)[[6]])

#PCS
PHC_val <- append(PHC_val, t.test(thesis_NHRVS$PCS~thesis_NHRVS$Any_PHC)[[1]])
PHC_p <- append(PHC_p, t.test(thesis_NHRVS$PCS~thesis_NHRVS$Any_PHC)[[3]])

#MCS
PHC_val <- append(PHC_val, t.test(thesis_NHRVS$MCS~thesis_NHRVS$Any_PHC)[[1]])
PHC_p <- append(PHC_p, t.test(thesis_NHRVS$MCS~thesis_NHRVS$Any_PHC)[[3]])

#BMI
PHC_val <- append(PHC_val, t.test(thesis_NHRVS$BMI~thesis_NHRVS$Any_PHC)[[1]])
PHC_p <- append(PHC_p, t.test(thesis_NHRVS$BMI~thesis_NHRVS$Any_PHC)[[3]])

#Combat_Veteran
Combat_Veteran_test_PHC<- xtabs(~Any_PHC+Combat_Veteran, data=thesis_NHRVS)
PHC_val <- append(PHC_val,summary(Combat_Veteran_test_PHC)[[3]])
PHC_p <- append(PHC_p,summary(Combat_Veteran_test_PHC)[[6]])

#Yr5_Military
Yr5_Military_test_PHC<- xtabs(~Any_PHC+Yr5_Military, data=thesis_NHRVS)
PHC_val <- append(PHC_val,summary(Yr5_Military_test_PHC)[[3]])
PHC_p <- append(PHC_p,summary(Yr5_Military_test_PHC)[[6]])

#TOTAL TRAUMAS
PHC_val <- append(PHC_val, t.test(thesis_NHRVS$TOTAL_TRAUMAS~thesis_NHRVS$Any_PHC)[[1]])
PHC_p <- append(PHC_p, t.test(thesis_NHRVS$TOTAL_TRAUMAS~thesis_NHRVS$Any_PHC)[[3]])

#TOTAL Physical Health Conditions
PHC_val <- append(PHC_val, t.test(thesis_NHRVS$tot_phc~thesis_NHRVS$Any_PHC)[[1]])
PHC_p <- append(PHC_p, t.test(thesis_NHRVS$tot_phc~thesis_NHRVS$Any_PHC)[[3]])

t.test(thesis_NHRVS$tot_phc~thesis_NHRVS$Any_PHC)

#TOTAL Mental Health Conditions
PHC_val <- append(PHC_val, t.test(thesis_NHRVS$tot_MHC~thesis_NHRVS$Any_PHC)[[1]])
PHC_p <- append(PHC_p, t.test(thesis_NHRVS$tot_MHC~thesis_NHRVS$Any_PHC)[[3]])

# Combine into one DF
val_df <- cbind(val_df,PHC_val,PHC_p)

#### Create test of difference values and put them into a table
#Age
MHC_val <- c(t.test(thesis_NHRVS$Age~thesis_NHRVS$Any_MHC)[[1]])
MHC_p <- c(t.test(thesis_NHRVS$Age~thesis_NHRVS$Any_MHC)[[3]])

#Gender
Male_test_MHC<- xtabs(~Any_MHC+Male_Gender, data=thesis_NHRVS)
summary(Male_test_MHC)
MHC_val <- append(MHC_val,Male_test_MHC[[3]])
MHC_p <- append(MHC_p,summary(Male_test_MHC)[[6]])

#White
White_test_MHC<- xtabs(~Any_MHC+White_Race, data=thesis_NHRVS)
MHC_val <- append(MHC_val,summary(White_test_MHC)[[3]])
MHC_p <- append(MHC_p,summary(White_test_MHC)[[6]])

#some College
College_test_MHC<- xtabs(~Any_MHC+College, data=thesis_NHRVS)
MHC_val <- append(MHC_val,summary(College_test_MHC)[[3]])
MHC_p <- append(MHC_p,summary(College_test_MHC)[[6]])

#Married_Partnered
Married_Partnered_test_MHC<- xtabs(~Any_MHC+Married_Partnered, data=thesis_NHRVS)
MHC_val <- append(MHC_val,summary(Married_Partnered_test_MHC)[[3]])
MHC_p <- append(MHC_p,summary(Married_Partnered_test_MHC)[[6]])

#Income_60k_plus
Income_60k_plus_test_MHC<- xtabs(~Any_MHC+Income_60k_plus, data=thesis_NHRVS)
MHC_val <- append(MHC_val,summary(Income_60k_plus_test_MHC)[[3]])
MHC_p <- append(MHC_p,summary(Income_60k_plus_test_MHC)[[6]])

#YN_work
YN_work_test_MHC<- xtabs(~Any_MHC+YN_work, data=thesis_NHRVS)
MHC_val <- append(MHC_val,summary(YN_work_test_MHC)[[3]])
MHC_p <- append(MHC_p,summary(YN_work_test_MHC)[[6]])

#PCS
MHC_val <- append(MHC_val, t.test(thesis_NHRVS$PCS~thesis_NHRVS$Any_MHC)[[1]])
MHC_p <- append(MHC_p, t.test(thesis_NHRVS$PCS~thesis_NHRVS$Any_MHC)[[3]])

#MCS
MHC_val <- append(MHC_val, t.test(thesis_NHRVS$MCS~thesis_NHRVS$Any_MHC)[[1]])
MHC_p <- append(MHC_p, t.test(thesis_NHRVS$MCS~thesis_NHRVS$Any_MHC)[[3]])

#BMI
MHC_val <- append(MHC_val, t.test(thesis_NHRVS$BMI~thesis_NHRVS$Any_MHC)[[1]])
MHC_p <- append(MHC_p, t.test(thesis_NHRVS$BMI~thesis_NHRVS$Any_MHC)[[3]])

#Combat_Veteran
Combat_Veteran_test_MHC<- xtabs(~Any_MHC+Combat_Veteran, data=thesis_NHRVS)
MHC_val <- append(MHC_val,summary(Combat_Veteran_test_MHC)[[3]])
MHC_p <- append(MHC_p,summary(Combat_Veteran_test_MHC)[[6]])

#Yr5_Military
Yr5_Military_test_MHC<- xtabs(~Any_MHC+Yr5_Military, data=thesis_NHRVS)
MHC_val <- append(MHC_val,summary(Yr5_Military_test_MHC)[[3]])
MHC_p <- append(MHC_p,summary(Yr5_Military_test_MHC)[[6]])

#TOTAL TRAUMAS
MHC_val <- append(MHC_val, t.test(thesis_NHRVS$TOTAL_TRAUMAS~thesis_NHRVS$Any_MHC)[[1]])
MHC_p <- append(MHC_p, t.test(thesis_NHRVS$TOTAL_TRAUMAS~thesis_NHRVS$Any_MHC)[[3]])

#TOTAL Physical Health Conditions
MHC_val <- append(MHC_val, t.test(thesis_NHRVS$tot_MHC~thesis_NHRVS$Any_MHC)[[1]])
MHC_p <- append(MHC_p, t.test(thesis_NHRVS$tot_MHC~thesis_NHRVS$Any_MHC)[[3]])

#TOTAL Physical Health Conditions
MHC_val <- append(MHC_val, t.test(thesis_NHRVS$tot_phc~thesis_NHRVS$Any_MHC)[[1]])
MHC_p <- append(MHC_p, t.test(thesis_NHRVS$tot_phc~thesis_NHRVS$Any_MHC)[[3]])
```

#### Combine into one table

Now that we have the test of differences for our covariates by physical activity level, and physical/ mental health conditions we can combine them into one table. 
```{r}
val_df <- cbind(val_df,PHC_val,PHC_p)
val_df <- cbind(val_df,MHC_val,MHC_p)

kbl(val_df) %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

### Export to CSV
```{r}
write_csv(val_df, "~/Desktop/Coding/data/thesis_test_dif.csv" )
```


