---
title: "Thesis Forrest Plots"
output: html_document
date: "2023-02-18"
---

```{r,include=FALSE}
# knit: (function(input_file, encoding) {
#     out_dir <- 'docs';
#     rmarkdown::render(input_file,
#       encoding=encoding,
#       output_file=file.path(dirname(input_file), out_dir, 'index.html'))})

#one day we will use this??
```

      
This markdown shows the steps taken to make detailed Forrest plots for several 
multinomial regressions. This includes variable names, the Odds ratios (OR), and 
their associated P values. Results for the current study are from the following 
publication:

Hubert T., Adams T., Pizerkt R., (In Preparation) Associations between Physical Activity Levels and Physical and Mental Health and Illness in U.S. Military Veterans: Results from the 2019/2020 National Health and Resilience in Veterans Study.

## Study design

The current study is examining how physical and mental health conditions are 
associated with levels of physical activity (e.g., insufficiently active, moderately
active, and sufficiently active). The proposed study used several 
multinomial logistic regressions to evaluate the odds of being in each physical 
activity level when reporting a health condition. As such, the code below creates 
three Forrest plots displaying the odds of reporting each condition between each 
gorup relative to another. 

```{r, include=FALSE}
## load up the packages we will need: 
library(tidyverse)

library(gt)
# for putting ggplots together
library(patchwork)
# for reordering facctors in ggplot
library(forcats)
## ---------------------------
```

## load data
First thing to do is to load the data into R. I have already created tables 
with all of the values needed for these plots. You can find my code my code to 
make the tables <HERE>
```{r}
#### MET MINS
Ins_Mod <- read_csv("~/Desktop/Coding/data/Ins_Mod.csv")
Ins_Act <- read_csv("~/Desktop/Coding/data/Ins_Act.csv")
Act_Mod <- read_csv( "~/Desktop/Coding/data/Act_Mod.csv")

# Ins_Act <- Ins_Act[2:24,]
# Act_Mod <- Act_Mod[2:24,]
Ins_Act
Ins_Mod
Act_Mod
```

Because GGplot likes to sort things based upon its own "standards" we need to create 
a variable (i.e., order) and manually assign the order that we want the plot and 
values to be in. Additionally, I wanted to assign a variable that indicates which 
ORs were significant after alpha corrections, so I created a variable (i.e., sig) 
that we can use to color the significaant values later on.
```{r}
#create the variable within the dataframe
Ins_Mod <- mutate(Ins_Mod, order = 0)
#update the values of the dataset to reflect the order we want
Ins_Mod[1,9]  = 2
Ins_Mod[2,9]  = 3
Ins_Mod[3,9]  = 4
Ins_Mod[4,9]  = 5
Ins_Mod[5,9]  = 6
Ins_Mod[6,9]  = 7
Ins_Mod[7,9]  = 8
Ins_Mod[8,9]  = 9
Ins_Mod[9,9]  = 10
Ins_Mod[10,9] = 11
Ins_Mod[11,9] = 12
Ins_Mod[12,9] = 13
Ins_Mod[13,9] = 14
Ins_Mod[14,9] = 15
Ins_Mod[15,9] = 16
Ins_Mod[16,9] = 17
Ins_Mod[17,9] = 18
Ins_Mod[18,9] = 19
Ins_Mod[19,9] = 20
Ins_Mod[20,9] = 21
Ins_Mod[21,9] = 22
Ins_Mod[22,9] = 23
Ins_Mod[23,9] = 24

# create a varaible for significance 
Ins_Mod <- mutate(Ins_Mod, sig = 0)
```


```{r}
# assign values to the significant models post alpha corrections.
Ins_Mod[1,10] = 1
Ins_Mod[3,10] = 1
Ins_Mod[5,10] = 1
Ins_Mod[21,10] = 1
```

We are going to split these conditions into a mental and physical health dataframes.
because GGplot gets mad when we try to arrange these all together. 
```{r}
phc_IM <- Ins_Mod[1:17,]
mhc_IM <- Ins_Mod[18:23,]
phc_IM
mhc_IM
```
Now we have a data frame for physical health conditions and a data frame for mental 
health conditions. We will repeat these steps for the other 2 models.

```{r, include=FALSE}
Ins_Act <- mutate(Ins_Act, order = 0)
Ins_Act[1,9]  = 2
Ins_Act[2,9]  = 3
Ins_Act[3,9]  = 4
Ins_Act[4,9]  = 5
Ins_Act[5,9]  = 6
Ins_Act[6,9]  = 7
Ins_Act[7,9]  = 8
Ins_Act[8,9]  = 9
Ins_Act[9,9]  = 10
Ins_Act[10,9] = 11
Ins_Act[11,9] = 12
Ins_Act[12,9] = 13
Ins_Act[13,9] = 14
Ins_Act[14,9] = 15
Ins_Act[15,9] = 16
Ins_Act[16,9] = 17
Ins_Act[17,9] = 18
Ins_Act[18,9] = 2
Ins_Act[19,9] = 3
Ins_Act[20,9] = 4
Ins_Act[21,9] = 5
Ins_Act[22,9] = 6
Ins_Act[23,9] = 7
Ins_Act

Ins_Act <- mutate(Ins_Act, sig = 0)
Ins_Act[1,10] = 1
Ins_Act[3,10] = 1
Ins_Act[5,10] = 1
Ins_Act[6,10] = 1
Ins_Act[7,10] = 1
Ins_Act[9,10] = 1
Ins_Act[15,10] = 1
Ins_Act[17,10] = 1
Ins_Act[19,10] = 1
Ins_Act[20,10] = 1
Ins_Act[21,10] = 1

phc_IA <- Ins_Act[1:17,]
mhc_IA <- Ins_Act[18:23,]
```

```{r, include=FALSE}
Act_Mod <- mutate(Act_Mod, order = 0)
Act_Mod[1,9] = 2
Act_Mod[2,9] = 3
Act_Mod[3,9] = 4
Act_Mod[4,9]  = 5
Act_Mod[5,9]  = 6
Act_Mod[6,9]  = 7
Act_Mod[7,9]  = 8
Act_Mod[8,9]  = 9
Act_Mod[9,9]  = 10
Act_Mod[10,9] = 11
Act_Mod[11,9] = 12
Act_Mod[12,9] = 13
Act_Mod[13,9] = 14
Act_Mod[14,9] = 15
Act_Mod[15,9] = 16
Act_Mod[16,9] = 17
Act_Mod[17,9] = 18
Act_Mod[18,9] = 2
Act_Mod[19,9] = 3
Act_Mod[20,9] = 4
Act_Mod[21,9] = 5
Act_Mod[22,9] = 6
Act_Mod[23,9] = 7

Act_Mod <- mutate(Act_Mod, sig = 0)

phc_AM <- Act_Mod[1:17,]
mhc_AM <- Act_Mod[18:23,]
```

## Middle: Create The Plot

Now that we have the data all ready, we can create the plot. For the forrest plot 
I am going to save the output of the plot into "phc_IA_mid". As I am repeating the 
same plot 3 times, for both mental and physical health conditions I want my code to 
be clear. We create the forrest plot with geom point & geom linerange, and I have 
added color to signify which conditions were significant after corrections. 
#### Forrest Plot Function

```{r,include=FALSE}
# Ins__plot <- Ins_Mod |>
#   #Plot the value variable (in descending order) assigning significance to the 
#   #values significant after Bon foroni alpha corrections
#   ggplot(aes(y = reorder(variable, -order),color = as.factor(sig))) +
#   #take away background
#   theme_classic() +
#   #make the forrest plot
#   geom_point(aes(x=estimate), shape=15, size=3,show.legend = FALSE) +
#   geom_linerange(aes(xmin=conf.low, xmax=conf.high),show.legend = FALSE) +
#   #add color 
#   scale_color_manual(values = c("#A6A6A6","blue"))+
#   #change Cordinates
#   labs(x="Odds Ratio") +
#   #adjust the dimentions. 
#   coord_cartesian(ylim = c(1,24), xlim=c(.25, 1.75)) +
#   #add a line at 0 for reference 
#   geom_vline(xintercept = 1, linetype="dashed") +
#   #add anotations to help suggests what each side means.
#   annotate("text", x = .5, y = 18, label = "Less Likely") +
#   annotate("text", x = 1.5, y = 18, label = "More Likely") 
#   #Git rid of the Y - Axis
# Ins_act_plot
```

```{r}
mid_Fplot <-function(data){
output <- data |>
  #Plot the value variable (in descending order) assigning significance to the 
  #values significant after Bon foroni alpha corrections
  ggplot(aes(y = reorder(variable, -order),color = as.factor(sig))) +
  #take away background
  theme_classic() +
  #make the forrest plot
  geom_point(aes(x=estimate), shape=15, size=3,show.legend = FALSE) +
  geom_linerange(aes(xmin=conf.low, xmax=conf.high),show.legend = FALSE) +
  #add color 
  scale_color_manual(values = c("#A6A6A6","blue"))+
  #change Cordinates
  labs(x="Odds Ratio") +
  #adjust the dimentions. 
  coord_cartesian(ylim = c(1,18), xlim=c(.25, 1.75)) +
  #add a line at 0 for reference 
  geom_vline(xintercept = 1, linetype="dashed") +
  #add anotations to help suggests what each side means.
  annotate("text", x = .5, y = 18, label = "Less Likely") +
  annotate("text", x = 1.5, y = 18, label = "More Likely") +
  #Git rid of the Y - Axis
  theme(axis.line.y = element_blank(),
        axis.ticks.y= element_blank(),
        axis.text.y= element_blank(),
        axis.title.y= element_blank())
return (output)
}
```


#### Applying the function
As we separated the datasets into mental health and physical health data frames, we can just call one function to do both parts of the plots.
```{r}
#Physical Health Conditions
phc_IA_mid<-mid_Fplot(phc_IA)
#Mental Health Conditions
mhc_IA_mid<- mid_Fplot(mhc_IA)
phc_IA_mid
mhc_IA_mid
```

No repeat this for the other 4 plots.
```{r}
# Insufficient vs Moderate
phc_IM_mid <- mid_Fplot(phc_IM)
mhc_IM_mid <- mid_Fplot(mhc_IM)
# Active vs Moderate
phc_AM_mid <- mid_Fplot(phc_AM)
mhc_AM_mid <- mid_Fplot(mhc_AM)
```
       
       
We have our plots! We can interpret this as, "Compared to veterans who were are insufficient active, veterans who were moderately active were (less/no difference/more) likely to report X health condition." For these figures the blue lines indicate which health conditions are significant after alpha corrections. 
```{r}
#Physical Health Conditions
phc_IA_mid
#Mental Health Conditions
mhc_IA_mid
```

## Left Side: labels for the forrest plot

We took away the standard y axis of GGplot because it is simplistic. Now we are 
now going to add a Y axis that includes the variable names (i.e., Health Conditions) 
and their respective ORs.

#### Update data frame
The output from the statistical models (e.g., p values) is not rounded to clean 
numbers. The code below tidy's up our data and creates new values. Additionally
our table has seperate values for OR, and 95% CI. The code below combines these
values into one variable so we can call it for the table.

```{r}
DF_update <- function(data){
#assign the input and output of the data
output <-data |>
  # round estimates and 95% CIs to 2 decimal places for journal specifications
  mutate(across(
    c(estimate, conf.low, conf.high),
    ~ str_pad(
      round(.x, 2),
      width = 4,
      pad = "0",
      side = "right"
    )
  ),
  # add an "-" between HR estimate confidence intervals
  estimate_lab = paste0(estimate, " (", conf.low, "-", conf.high, ")")) |>
  # round p-values to two decimal places, except in cases where p < .001
  mutate(p.value = case_when(
    p.value < .001 ~ "<0.001",
    round(p.value, 2) == .05 ~ as.character(round(p.value,3)),
    p.value < .01 ~ str_pad( # if less than .01, go one more decimal place
      as.character(round(p.value, 3)),
      width = 4,
      pad = "0",
      side = "right"
    ),
    TRUE ~ str_pad( # otherwise just round to 2 decimal places and pad string so that .2 reads as 0.20
      as.character(round(p.value, 2)),
      width = 4,
      pad = "0",
      side = "right"
    )
  )) |>
  # add a row of data that are actually column names which will be shown on the plot in the next step
  bind_rows(
    data.frame(
      variable = "Condition",
      estimate_lab = "Odd Ratio (95% CI)",
      conf.low = "",
      conf.high = "",
      p.value = "p-value"
    )
  ) |>
  mutate(model = fct_rev(fct_relevel(variable, "Condition")))
# have the funciton spit out the new data
return(output)
}
```

Now that we have made a function, lets see what it does.
```{r}
# Insufficient vs Active
phc_IA_plot <- DF_update(phc_IA)
  #double check to make sure it worked.
glimpse(phc_IA_plot$estimate_lab)
```


Update the rest of the data frames
```{r}
mhc_IA_plot <- DF_update(mhc_IA)

# Insufficient vs moderate
phc_IM_plot <- DF_update(phc_IM)
mhc_IM_plot <- DF_update(mhc_IM)

# active vs moderate
phc_AM_plot <- DF_update(phc_AM)
mhc_AM_plot <- DF_update(mhc_AM)
```

### Plotting the left side

Now that we have the variables int he format for the plot, we can plot it! 
```{r}
left_FP <- function(plot_data,type){
  # For Physical health condition plots
  if(type == "PHC") {
    # add the top row
    plot_data<-mutate(plot_data, top_row = 0)
    plot_data[18,9] = 1
    plot_data <- arrange(plot_data,order)

    # plot the left side of the plot 
    output <- plot_data %>% 
      ggplot(aes(y = model)) +
      geom_text(aes(x = 0, label = variable), hjust = 0, fontface = "bold")+
      geom_text(
      aes(x = 1, label = estimate_lab),
      hjust = 0,
      fontface = ifelse(phc_IA_plot$estimate_lab == "Odds Ratio (95% CI)", "bold","plain")) +
      theme_void() +
      coord_cartesian(ylim = c(1,18), xlim = c(0, 4))
  }
  # For Mental health condition plots
  if(type == "MHC"){
    #arange the labels on top
      plot_data<-mutate(plot_data, top_row = 0)
      plot_data[7,9] = 1
      plot_data <- arrange(plot_data,order)

    # plot the left side of the plot 
      output <- plot_data %>% 
        ggplot(aes(y = model)) +
        geom_text(aes(x = 0, label = variable), hjust = 0, fontface = "bold")+
        geom_text(aes(x = 1, label = estimate_lab),
        hjust = 0,
        fontface = ifelse(mhc_IA_plot$estimate_lab == "Odds Ratio (95% CI)", "bold","plain")) +
        theme_void() +
        coord_cartesian(ylim = c(1,18), xlim = c(0, 4))
  }
  return(output)
}
```
Run the function
```{r}
phc_IA_left<-left_FP(phc_IA_plot,"PHC")
mhc_IA_left<-left_FP(mhc_IA_plot,"MHC")
phc_IM_left<-left_FP(phc_IM_plot,"PHC")
mhc_IM_left<-left_FP(mhc_IM_plot,"MHC")
phc_AM_left<-left_FP(phc_AM_plot,"PHC")
mhc_AM_left<-left_FP(mhc_AM_plot,"MHC")
```
Now we have our labels. In our labels we have the name of our conditions and the OR + 95 CI.
```{r}
phc_IA_left
mhc_IA_left
```

## Right: P values 

We now have the left side and the middle of the plot. The last thing we need is 
to show the P values on the right side of the table. We have already updated our 
data frame (above) so now we can just put them in the figure like how we did for 
the left side.


```{r}
right_FP<-function(plot_data){
    output <- plot_data |>
      ggplot() +
        geom_text(aes(x = 0, y = model, label = p.value), hjust = 0,
        fontface = ifelse(plot_data$p.value == "p-value", "bold", "plain")) +
        theme_void() +
        coord_cartesian(ylim = c(1,18))
return(output)
}
```

run the function
```{r}
phc_IA_right <- right_FP(phc_IA_plot)
mhc_IA_right <- right_FP(mhc_IA_plot)
phc_IM_right <- right_FP(phc_IM_plot)
mhc_IM_right <- right_FP(mhc_IM_plot)
phc_AM_right <- right_FP(phc_AM_plot)
mhc_AM_right <- right_FP(mhc_AM_plot)
```

Example of the p value output
```{r}
phc_IA_right
mhc_IA_right
```

## Putting It Together
We now have all of the pieces of the puzzle. Now we need to specify how much area
all of these individual parts will take up in the final output. Below we specify where
each of the individual plots starts and finishes. t = top, l = left, b = bottom, 
r = right. We assign these to a a vector (e.g.layout) for the plot.

```{r}
layout <- c(
  patchwork::area(t = 0, l = 0, b = 30, r = 25),
  patchwork::area(t = 0, l = 14, b = 30, r = 25),
  patchwork::area(t = 0, l = 23, b = 30, r = 30) 
  )

```

### final plot arrangement
Combine all of the parts together to get the final product! You may notice or 
be wondering why the mental health plot is so weirdly formatted. This is because
I will be moving them over to illustrator to combine the plots together to look
like one cohesive plot. I gave up in GGplot. 

## Likelihood of reporting health conditions for veterans with sufficient physical activity compared to insufficient activity.
```{r}
# physical health conditions. - Ins vs Mod
phc_IA_left + phc_IA_mid + phc_IA_right + plot_layout(design = layout)
```

#### Note.

Compared to veterans who are insufficiently active, those who are sufficiently
active are less likely to report any disability, asthma, chronic pain, diabetes, 
and hypertension. No other differences were observed between the odds of
reporting other conditions between insufficient and moderate activity. 

```{r}
mhc_IA_left + mhc_IA_mid + mhc_IA_right + plot_layout(design = layout)
```

#### Note.
Compared to veterans who are insufficiently active, those who are sufficiently
active are more likely to report PTSD.

## Likelihood of reporting health conditions for veterans with moderate physical activity compared to insufficient activity.

```{r}
### Ins vs. Mod
phc_IM_left + phc_IM_mid + phc_IM_right + plot_layout(design = layout)
```

#### Note. 
Compared to veterans who are insufficiently active, those who are moderately
active are less likely to report any disability, asthma, chronic pain, diabetes, 
high cholesterol, and stroke. No other differences were observed between the odds of
reporting other conditions between insufficient and moderate activity.

```{r}
mhc_IM_left + mhc_IM_mid + mhc_IM_right + plot_layout(design = layout)
```

#### Note 
Compared to veterans who are insufficiently active, those who are moderately
active are less likely to report nicotine dependence. No other differences were observed between the odds of
reporting other conditions between insufficient and moderate activity.


## Likelihood of reporting health conditions for veterans with sufficient physical activity compared to moderate activity.

```{r}
phc_AM_left + phc_AM_mid + phc_AM_right + plot_layout(design = layout)
```

#### Note
No other differences were observed between the odds of
reporting physical health conditions between insufficient and moderate activity.

```{r}
mhc_AM_left + mhc_AM_mid + mhc_AM_right + plot_layout(design = layout)

```

#### Note

No other differences were observed between the odds of
reporting mental health conditions between insufficient and moderate activity.


## Save the plots as png

```{r,results='hide'}
png(file="IvA_phc.png",
width=700, height=450)
phc_IA_left + phc_IA_mid + phc_IA_right + plot_layout(design = layout)
dev.off()

png(file="IvA_mhc.png",
width=700, height=450)
mhc_IA_left + mhc_IA_mid + mhc_IA_right + plot_layout(design = layout)
dev.off()

png(file="IvM_phc.png",
width=700, height=450)
phc_IM_left + phc_IM_mid + phc_IM_right + plot_layout(design = layout)
dev.off()

png(file="IvM_mhc.png",
width=700, height=450)
mhc_IM_left + mhc_IM_mid + mhc_IM_right + plot_layout(design = layout)
dev.off()

png(file="AvM_phc.png",
width=700, height=450)
phc_AM_left + phc_AM_mid + phc_AM_right + plot_layout(design = layout)
dev.off()

png(file="AvM_mhc.png",
width=700, height=450)
mhc_AM_left + mhc_AM_mid + mhc_AM_right + plot_layout(design = layout)
dev.off()
```


